From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/acl2020_main.tex
[ACL2020] abstract
minor tweaks here and there

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
Our analyses also demonstrate the challenges of collecting data of language phenomena that is a proxy for real-world situations in which the phenomenon under occurs.  
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\sz{something ...}
\end{abstract}

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges.

>>>>

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
%Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\end{abstract}

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges.

### 2019-12-10 papers/ACL2020/analysis.tex
minor tweaks here and there

\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples):\\
Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:
\begin{tabularx}{.49\textwidth}{lX}
	\sameobject: & an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	OtherObject & a name produced by annotators, but not an alternative of the entry-level name \\
	LowCount: & a name produced by one annotator\\
	Related:& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
\end{tabularx}
\iffalse
\begin{itemize}
	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
	\item LowCount: a name produced by only one annotator
	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
\end{itemize}
\fi

Semantically related names are determined with WordNet \cite{fellbaum1998wordnet}.

@@

Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. The proportion of human-like error is suprisingly constant across all models.
Both object detection models essentially achieve the same portion of human-like mishits. Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse semantically similar names to a valid name, that are, however, not valid.

\iffalse
\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll||rr|rrr}
\toprule
&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
                         model &  gt &  hit &  valid &  human-like &  related &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
        \midrule
 FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
         \midrule
         %ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
         ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
     	ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\

\bottomrule
\end{tabular}

\caption{Model results for different categories of errors} \label{tab:humanlike}
\end{table*}
\fi

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll|rrr|rrr}
\toprule
&  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
                         model &  GT &  hit &  human-like &  off &  hit &  human-like &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &           2.6 &      2.6 &   63.6 &          30.9 &      5.5 \\
        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &           4.2 &      6.2 &   60.7 &          31.3 &      8.0 \\
        \midrule
 	FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &           4.2 &      1.3 &   72.9 &          22.7 &      4.4 \\
 \midrule
 %ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
 ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &           6.2 &      5.5 &   48.5 &          38.8 &     12.7 \\
    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &           5.2 &      6.2 &   49.9 &          38.2 &     12.0 \\
\bottomrule
\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{human-like} error (less preferred name, synonym, hypernym/hyponym), or \textit{off} \label{tab:exp_errors_agreement}}
\end{table*}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{l|l|c@{~}c@{~}c@{~}c}
		\toprule
		{Model} &  GT & visual &  linguistic &  box &  other \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
		FRCNN$_{\text{MN442}}$ & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
		\midrule
		FRCNN$_{\text{VG1600--VGMN}}$ & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
		\midrule
		%ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
		ResNet101$_{\text{VGMN}}$ & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
		\bottomrule
	\end{tabular}
	\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
\end{table}
\iffalse
\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}

	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes} \gbt{Will we have space for the figure? (Maybe we should \textit{make} space?) Also, shouldn't we put examples from the most successful model instead?}}
\end{figure}
\fi 
\paragraph{Do Predictions Deteriorate with Agreement?}
%An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
%This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.

In Table \ref{tab:exp_errors_agreement}, we show the break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name. 
Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
Note that this even holds for the ResNet-based classifiers that generally achieve less accuracy.
When agreement is lower, all models produce less hits and more valid alternatives. 
This indicates that there is indeed a certain similarity between what is difficult for humans and models.
%Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\

In Table~\ref{tab:exp_inadequacy} we focus on the predicted \mn names that were judged as inadequate (i.e.,~adequacy score\mbox{$<0.5$}) and their inadequacy types (see Section~\ref{sect:mn_analysis}.
Most of the inadequate name predictions are related to an inaccurate bounding box. 
The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of box errors, but the highest \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions. 
An example for this is shown in Figure \ref{fig:mistakes} (right): FRCNN$_{\text{VG1600--VGMN}}$  predicts a more specific \textit{cow} for an object that most humans and FRCNN$_{\text{VG1600}}$ named \textit{animal}.
This illustrates an extremely tricky case of entry-level name: the model essentially has to guess that humans will have difficulties naming that object with a specific or basic-level name and opt instead for an unusually general name.

%This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
\iffalse
\cs{remove next couple of sentences? it's very assumptive}
This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts. 
\fi
%
None of the models predicted an inadequate name that was a linguistic, or any other error. 
Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on MN illustrates the challenges involved in collecting object names from image data to model natural object naming, and the relevance of thorough verification and quality control as we did in our work.

>>>>

\paragraph{Error Categories} We categorize model predictions into several types (see also Figure~\ref{fig:mistakes} for examples).
Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name), we distinguish between different \textit{Human-like mishits}:
\begin{tabularx}{.49\textwidth}{lX}
	\textbf{\sameobject:} & alternative name for the same object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
	\end{tabularx}
\begin{tabularx}{.49\textwidth}{lX}
	\textbf{LowCount:} & name produced by 1 annotator\\
	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
\end{tabularx}
Semantically related names are determined with WordNet \cite{fellbaum1998wordnet}. 
%\iffalse
%\begin{itemize}
%	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
%	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
%	\item LowCount: a name produced by only one annotator
%	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
%\end{itemize}
%\fi

@@

Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. The proportion of human-like error is suprisingly constant across all models.
Both object detection models achieve essentially the same portion of human-like mishits. Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but fewer valid predictions, and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.

%\iffalse
%\begin{table*}[t]
%\centering
%	\small
%\begin{tabular}{ll||rr|rrr}
%\toprule
%&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
%                         model &  gt &  hit &  valid &  human-like &  related &  off \\
%\midrule
%       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
%        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
%        \midrule
% FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
%         \midrule
%         %ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
%         ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
%     	ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
%         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
%     
%\bottomrule
%\end{tabular}
%
%\caption{Model results for different categories of errors} \label{tab:humanlike}
%\end{table*}
%\fi

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll|rrr|rrr}
\toprule
&  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
                         model &  GT &  hit &  human-like &  off &  hit &  human-like &  off \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &           2.6 &      2.6 &   63.6 &          30.9 &      5.5 \\
        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &           4.2 &      6.2 &   60.7 &          31.3 &      8.0 \\
        \midrule
 	FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &           4.2 &      1.3 &   72.9 &          22.7 &      4.4 \\
 \midrule
 %ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
 ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &           6.2 &      5.5 &   48.5 &          38.8 &     12.7 \\
    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &           5.2 &      6.2 &   49.9 &          38.2 &     12.0 \\
\bottomrule
\end{tabular}
\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{human-like} error (less preferred name, synonym, hypernym/hyponym), or \textit{off} \label{tab:exp_errors_agreement}}
\end{table*}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{l|l|c@{~}c@{~}c@{~}c}
		\toprule
		{Model} &  GT & visual &  linguistic &  box &  other \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
		FRCNN$_{\text{MN442}}$ & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
		\midrule
		FRCNN$_{\text{VG1600--VGMN}}$ & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
		\midrule
		%ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
		ResNet101$_{\text{VGMN}}$ & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
		ResNet101$_{\text{MN442}}$ & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
		\bottomrule
	\end{tabular}
	\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
\end{table}
%\iffalse
%\begin{figure}
%	\centering
%	\includegraphics[scale=.2]{images/2323938.jpg}
%	\includegraphics[scale=.2]{images/2322259.jpg}
%	\includegraphics[scale=.2]{images/2371657.jpg}
%	
%	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes} \gbt{Will we have space for the figure? (Maybe we should \textit{make} space?) Also, shouldn't we put examples from the most successful model instead?}}
%\end{figure}
%\fi

\paragraph{Low Human Agreement, Worse Predictions?}
%An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
%This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.

Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name. 
Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
Note that this holds even for the ResNet-based classifiers that generally achieve lower accuracy.
When human agreement is lower, all models produce fewer hits and more valid alternatives, indicating a similarity between what is difficult for models and humans.
%Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\

Table~\ref{tab:exp_inadequacy} focuses on the predicted \mn names that were judged as inadequate (i.e.,~adequacy score \mbox{$<0.5$}) and their inadequacy types (see Section~\ref{sect:mn_analysis}).
Most of the inadequate name predictions are due to the model naming an object that does not properly fit the bounding box. 
The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of these bounding box errors, but the highest proportion of \textit{visual} errors (i.e.,~named object misinterpreted for something it's not). 
An example for this is shown in Figure \ref{fig:mistakes} (right): FRCNN$_{\text{VG1600--VGMN}}$ predicts the more specific name \textit{cow} for an object that is not strictly speaker a cow and which most humans and FRCNN$_{\text{VG1600}}$ named \textit{animal}.
This illustrates a tricky case of entry-level name: the model needs to `understand' that humans will have difficulties naming that object with a specific or basic-level name and opt instead for an unusually general name.

%This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
%\iffalse
%\cs{remove next couple of sentences? it's very assumptive}
%This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
%And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts. 
%\fi
%
None of the models predicted an inadequate name classified as a ``linguistic error'' or as ``other error''.
Recall that all predictions we are analyzing here concerned the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on MN illustrates the challenges involved in collecting object names from image data to model natural object naming, and the relevance of thorough verification and quality control as we did in our work.

### 2019-12-10 papers/ACL2020/manynames.tex
intro
minor tweaks here and there

Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
%% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 422 entry-level names of \mn meet.
These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
%% SHORTENING %%  (SD: .34).
Importantly, the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).

@@

%ManyNames was collected in four rounds of 9 annotators each.
%On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
%Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
%\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
Regarding our second reason (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\columnwidth]{images/stability_analytic.png}
	\caption{\% of objects for which the entry-level name can be confidently identified after gathering N names.}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the entry-level name (as defined on the basis of 36 names) to be the majority name among them with 95\% probability.
The blue line shows that, even after gathering 10 names, the entry-level name is sufficiently likely to be the majority name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
Gathering 20 names increases this to 78\%.
Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
the red line is computed by taking only names from the \cluster of the entry-level name into account.

by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
%% SHORTENING %% (An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)

>>>>

Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
%% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 442 entry-level names of \mn meet.
These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
%% SHORTENING %%  (SD: .34).
Importantly, the verified results support the same conclusion: 
even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).

@@

%ManyNames was collected in four rounds of 9 annotators each.
%On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
%Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
%\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
Regarding our second reason (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
\begin{figure}[t]
	\centering
	\includegraphics[width=.7\columnwidth]{images/stability_analytic.png}
	\caption{\% of objects for which the entry-level name can be confidently identified after gathering N names.}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the entry-level name (as defined on the basis of 36 names) to be the majority name among them with 95\% probability.
The blue line shows that, even after gathering 10 names, the entry-level name is sufficiently likely to be the majority name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
Gathering 20 names increases this to 78\%.
Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
the red line is computed by taking only names from the \cluster of the entry-level name into account, showing that, by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily (but not by much, since names for the wrong object tend not to be frequent anyway).
%% SHORTENING %% (An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)
